Reproduce analyses reported in: *Phenotypic evolution is more constrained in simpler food webs*

### 2019-01-14 analyses/reproduce_analyses.Rmd
moved reproduction of Fig. 4 to end of file.

```{r Egg-Parasitoid-Selection, echo=F}
eggptoid_plot_df <- eggegg_RF_Pref$absolute_fitness %>% 
  select(-sc.Diam, -sc.log.Clutch) %>%
  gather(ID, absolute_fitness, -sc.sqrt.Pref, -Foodweb) %>%
  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
  spread(Foodweb, absolute_fitness) %>%
  mutate(fitness_difference = Complex-Simple)

@@

>>>>

@@

# Reproduce Figure 4 in main text

```{r Egg-Parasitoid-Selection}
eggptoid_plot_df <- eggegg_RF_Pref$absolute_fitness %>% 
  select(-sc.Diam, -sc.log.Clutch) %>%
  gather(ID, absolute_fitness, -sc.sqrt.Pref, -Foodweb) %>%
  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
  spread(Foodweb, absolute_fitness) %>%
  mutate(fitness_difference = Complex-Simple)
